\TITLE

### 2023-03-06 paper/content.tex
update paper

\section{Introduction}
\label{sec:introduction}
Lawyers, laboratories, auditors or banks, in order to provide services, require data often containing sensitive personal information.

Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.
%JS co może prowadzic do nieintencjonalnego naruszenia rodo  
%SP dodałem na dole

Such personal information can be used deliberately or accidently (e.g., by theft) 
%JS kradzież to chyba inencjonalne
%SB zmieniłem na accidentaly
for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. 
In turn, it can lead to an unintentional violation of the GDPR or CCPA, profiled advertisements or even criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

@@

In such situations, customers may be reluctant to provide their personal information to the SP and thus resign from the service. Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients. Both parties are affected as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.
% SB END emphasise

@@

% We observe
We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.

@@

%\paragraph{Contributions}
%We contribute to the state of the art by:
The contribution of our paper is:
\begin{itemize}
\item proposing a novel protocol that:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous position with an option to start a dispute in case a misbehaviour of SP.
  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
  \item In conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user-experience and practicality}.
  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
\item Proposing a framework for analyzing fairness in fair-exchange protocols.
\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
\end{itemize}

% Our protocol simultaneously provides five main properties:

% \begin{itemize}
% \item Anonymity: the customer stays anonymous to all external observers throughout the transaction.
% \item Fairness: at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
% \item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
% \item Blockchain-obvious: the customer using our protocol does not need to interact with the blockchain directly; especially, he does not need to obtain funds and pay for the transaction fees, allowing the use of our protocol for non-technical users.
% \item TTP-less: 
% our protocol does not rely on a trusted third party to conduct transactions fairly. Only in case of a dispute, the centralised justice is involved, which can be instantiated either with courts and polices, or blockchain-based dispute resolution mechanisms as discussed in Section~\ref{sec:decentralised-justice}.
% \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
% \end{itemize}

@@

%\paragraph{Organisation}
The rest of this paper is organized as follows.
In Section~\ref{sec:related-works} we review related works. 
Then, in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, results availability, and anonymity.
Section~\ref{sec:protocol} provides detailed description of the protocol.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
Section~\ref{sec:discussion} discuss possible improvements in terms of crowd-sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), anonymous delivery, and formal verification.
Finally, Section~\ref{sec:conclusion} concludes the paper.

@@

@@

However, the protocol relies on strong assumptions, namely, the existence of a TTP and an DA, who does not misbehave or collude with either party.

\subsection{Fair exchange, anonymity, and physical products delivery} 
\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}

@@

Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol involving physical products, which guarantees anonymity of both buyer and seller. They achieve it with the introduction of an online TTP that validates coins and guarantees fairness.

Anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent (DA) who take a product from the SC and provide it to the DC.
Both cabinets provide access to the product by passwords to conceal the identity of the buyer and the seller.

The protocol works as follows: \begingroup
\renewcommand{\labelenumii}{\arabic{enumii}.}

\begin{enumerate}
    \item Both parties agree on the purchase details.
    \item The buyer buys a digital coin from his bank and validates it with the TTP.
    \item The buyer sends to the seller the purchase order and the digital signature made by TTP on the encrypted coins.
    \item The seller posts the product to the SC.
    \item The DA collects the product from the SC and posts it to the DC.
    \item The buyer collects the product from the DC using a password.
    \item The buyer checks if the product is the ordered one.
    \begin{itemize}
    \item[-] if yes 
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item The buyer sends the acknowledgment to the DC and decryption key to the seller.
        \item The seller redeems the coins from the bank.
        \end{enumerate}
    \item[-] if no
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item The DC is equipped with a video camera that records the moment when the buyer opens the package and lets the buyer signal the invalidity of the product, and so, sending the encrypted recording to the TTP. 
        \item The dispute is settled via TTP, optionally letting each party reveal its identity.
    \end{enumerate}
    \end{itemize}
\end{enumerate}
\endgroup

Besides the assumptions of the existence of the TTP and DA (similar to the previous protocol~\cite{mohammedalarajFairnessPhysicalProducts2012}), the protocol also assumes:

\begin{itemize}
    \item the buyer's and seller's banks enable confidential transactions, and both share a commit buffer where the value is locked until the transaction is finished;
    \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
    \item there exists an anonymous communication channel, and the SC and the DC protected by a passwords;
    \item the DC is equipped with a video camera that records the moment when the buyer opens the package and provides a way to submit the video to TTP in case of a dispute;
\end{itemize}

@@

However, since the system uses Ethereum, it achieves pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.

@@

Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} is the closest to our protocol, however, it uses TTP and does not consider disputes between parties.

The authors proposed many extensions to the protocol, namely, in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries). However, none of them is relevant to our use case. We want the SP to remain public so that the anonymous buyer can easily start a dispute. We assume just one package of physical materials. Moreover, the package is delivered from the buyer to the SP, not the other way around — as it's the case for most e-commerce transactions.

@@

Our protocol achieves stronger anonymity guarantees. Namely, we achieve anonymity by using either cash or privacy-preserving blockchains. Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of the aforementioned protocols.

Our protocol does not use its own delivery system. We assume that there is a way to anonymously deliver a package either via SP's drop box, a customer's trusted party. The improvement of the protocol to support anonymous physical delivery via courier is discussed in Section~\ref{sec:anonymous-delivery}.

Also, our protocol does not provide its own dispute-resolution mechanism as Themis does. However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party. 
%JS to warto podkreslic w dyskusji
It can be instantiated with either the local court or police, or one of the blockchain
dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan. 10, 2023)}, LTO Network\footnote{LTO Network, a hybrid blockchain application development platform for securing, verifying, and exchanging enterprise information, https://lto.network/, (last visited Jan. 17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.

@@

\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{table*}}{\begin{table}}
% \ifx\FORMAT\DOUBLECOLUMN
% \begin{table*}
% \else
% \begin{table}
% \fi
\centering
\newcommand{\YES}{\cellcolor{green!50}Yes}
\newcommand{\ID}{\cellcolor{green!25}Identity}
\newcommand{\PSEUDO}{\cellcolor{green!25}Pseudonym}
\newcommand{\ANON}{\cellcolor{green!50}Anonymity}
\newcommand{\NO}{\cellcolor{red!50}No}
\newcommand{\TTP}{\cellcolor{red!50}TTP}
\newcommand{\BC}{\cellcolor{green!50}BC}
\caption{Comparision of related works.}
\label{tab:comparision}
\setlength{\tabcolsep}{3pt}

@@

% \begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}

\hline
Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
\hline
Alaraj, 2012~\cite{mohammedalarajFairnessPhysicalProducts2012} & \YES & \NO & \YES & \TTP & \YES \\
\hline
Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} & \YES & \YES & \NO & \TTP & \YES \\
\hline
Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
\hline
Themis~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
\hline
Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
\hline
This paper & \YES & \YES & \YES & \BC & \YES \\
\hline

@@

\section{Building Blocks}\label{sec:building-blocks}
\subsection{Dispute resolution system}

@@

Some oracles provide the data like weather, soccer match result, stock
price, train delay, election results, and others—and they are the ones we
are interested in—providing the settlement of a submitted dispute.

@@

Such a decentralized, voluntary, and anonymous dispute resolution system might work for simple contracts violations like an eBay seller sending broken or wrong products or an Airbnb apartment being inadequate to the photos in the offer. However, it is hard to realize such a decentralized evaluation of health or legal services quality when expertise and privacy concerns are taken into account. Therefore, in our protocol, we take the more conservative approach and resolve disputes using local
justice system (police or court).

@@

    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction at a certain time. The actual implementation depends on the particular cryptocurrency and is discussed further section~\ref{payment-for-services}.

@@

\subsection{Payment for services}\label{payment-for-services}
Transactions between customers and SPs must be pegged to prevent proving one payment for multiple transactions. In other
words, we need a mechanism that uniquely associates a payment with the corresponding transaction.

Depending on the cryptocurrency, the link can be created in different
ways:
% continue reading from here
\begin{itemize}

\item separate address: each transaction derives a new address uniquely associated with the transaction. Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{Bitcoin Improvement Proposals, Hierarchical Deterministic Wallets, \url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}, (last visited Dec. 03, 2022)}.
\item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$. Each payment containing the such value in the memo is considered to pay for the transaction. In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
\end{itemize}

Both approaches have some advantages and disadvantages, but our protocol can abstract them away by treating them as some randomly generated unique number, often called \textit{nonce} (number once). The actual implementation depends on a particular blockchain.

In case of a dispute, there must be a way to prove to justice that the customer has paid for the transaction. As the proof of transaction is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains. Monero allows proving and checking payments via dedicated API\footnote{Monero, How to prove payment, \url{https://www.getmonero.org//resources/user-guides/prove-payment.html}, \LASTVISITED}. ZCash provides a mechanism called Payment Disclosure \cite{daviesIntroductionPaymentDisclosure2017}.

\subsection{Storage network}\label{storage-network}
Once the SP finishes its service, she has to provide the result to the customer. The most natural approach would be to send the result via e-mail or some dedicated platform. However, since the customer wants to stay anonymous and so does not want to expose his e-mail address nor IP address. Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in section ~\ref{sec:message-board}.

@@

To increase anonymity, the customer should use standard techniques to hide its IP address, such as gateway, VPN, proxy, or onion routing.

@@

While most blockchains could provide message board functionality, anonymous payments are not as prevalent. Especially a provable storage network is a functionality of a few specialized blockchains.

@@

\section{The Protocol}\label{sec:protocol}
In this section, we propose an abstract protocol for anonymous service provisioning without any assumptions about the underlying technologies. We define the requirements for each role and leave the choice of the technology to the developer. Later in the paper (section~\ref{sec:experiments}) we describe our implementation used for conducting experiments.

@@

\begin{itemize}
\item There exists PKI infrastructure:
    \begin{itemize}
        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP.
        \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}(\mathrm{C})}$ and the SP $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$.
        \item The SP's public key $\mathrm{pk}(\mathrm{SP})$ is publicly known.
    \end{itemize}

\item Both the customer and the SP:
    \begin{itemize}
        \item use common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
        \item has access to anonymous payments blockchain, message board, and storage network.
    \end{itemize}

\item The SP:
    \begin{itemize}
        \item accepts packages from unknown customers.
        \item accepts payments with anonymous cryptocurrencies as described in section~\ref{payment-for-services}.
    \end{itemize}

\item Justice:
    \begin{itemize}
        \item accepts as evidence in a dispute the $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{attestation}$ as described in section~\ref{fairness}.
    \end{itemize}

\item Anonymous payments blockchain:
    \begin{itemize}
        \item supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{sec:pseudo-anon}.
        \item supports uniquely identifying transaction either via separate address, memo field, or other similar mechanisms as described in section ~\ref{payment-for-services}. 
    \end{itemize}

@@

\noindent \textbf
{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, a randomly generated provision identifier used to anonymously track the provision throughout the protocol's steps, and the customer's public key $\mathrm{pk(C)}$ used to encrypt the result published on the public storage network.

@@

% \begin{eqnarray}
%   \quad L_{\mathrm{H}}(H) & \equiv & (\begin{array}[t]{l}H_{\mathrm{p}}, H_{\mathrm{o}}, H_{\mathrm{c}}, H_{\mathrm{r}}, H_{\mathrm{t}}, H_{\mathrm{e}}, H_{\mathrm{b}}, H_{\mathrm{d}},\\ H_{\mathrm{i}}, H_{\mathrm{l}}, H_{\mathrm{g}}, H_{\mathrm{s}}, H_{\mathrm{x}}, H_{\mathrm{m}}, H_{\mathrm{n}} \; )\end{array} \\
%   \quad L_{\mathrm{B}}(B) & \equiv & \big( L_{\mathrm{H}}(B_{\mathrm{H}}), \widetilde{L}_{\mathrm{T}}^*(B_{\mathbf{T}}), L_{\mathrm{H}}^*(\hyperlink{ommer_block_headers_B__U}{B_{\mathbf{U}}}) \big)
%   \end{eqnarray}

@@

also:
\(\mathrm{T}_\mathrm{issue} < \mathrm{T}_\mathrm{pay} < \mathrm{T}_\mathrm{provide}\)

@@

\item $\mathrm{cid}$ - content identifier as specified in section~\ref{storage-network}.
\item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
\end{itemize}

>>>>

\section{Introduction}
\label{sec:introduction}
Diagnostic services such as paternity tests, doping tests, or venereal disease tests are performed at diagnostic centres that require clients to provide biological materials such as blood, urine, stool, or saliva. Unfortunately, to process transactions, clients are often forced to reveal their identities. Such a combination of personal data with biological materials exposes clients to significant privacy risks.

Other examples of sensitive services are, legal services, such as legal advice that may require disclosure of the history of financial transactions and confidential legal documents.

Banking services, such as credit scoring, may require sensitive personal data, such as medical records, and history of financial transactions.

Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.

Such personal information can be used deliberately or accidently (e.g., by theft) 
for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. 
In turn, it can lead to an unintentional violation of the GDPR or CCPA, profiled advertisements or even criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

@@

In such situations, customers may be reluctant to provide their personal information to the SP and thus resign from the service. Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients. Both parties are affected as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.

@@

We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.

@@

The contribution of our paper is:
\begin{itemize}
\item proposing a novel protocol that:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous position with an option to start a dispute in case a misbehaviour of SP.
  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
  \item In conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user-experience and practicality}.
  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
\item Proposing a framework for analyzing fairness in fair-exchange protocols.
\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
\end{itemize}

@@

The rest of this paper is organized as follows.
In Section~\ref{sec:related-works} we review related works. 
Then, in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, results availability, and anonymity.
Section~\ref{sec:protocol} provides detailed description of the protocol.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
Section~\ref{sec:discussion} discuss possible improvements in terms of crowd-sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), anonymous delivery, and formal verification.
Finally, Section~\ref{sec:conclusion} concludes the paper.

@@

To our best knowledge, the first system that allowed for fair exchange of physical products was proposed by Zhang et al. in 2006~\cite{zhangPracticalFairExchangeEPayment2006}. The protocol uses buyer's bank as TTP, and assumes no coalition between parties to achieve anonymity. 
Authors of

@@

However, the protocol relies on strong assumptions, namely, the existence of a TTP and an DA, who does not misbehave or collude with either party. Also the fairness is obtained assuming resilient communication channels.

\subsection{Fair exchange, anonymity, dispute resolution, and physical products delivery} 
\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}

@@

Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol involving physical products, which guarantees anonymity of both buyer and seller. They achieve it with the introduction of an online TTP that validates coins and guarantees fairness. Later, they proposed many extensions to the protocol, namely, in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries). Finally in~\cite{birjoveanuTwoPartyECommerceProtocols2022} they proposed improved protocol named PPPDCP (Protocol with Physical Product Delivery Providing Customer's Privacy).

Anonymity is ensured by using anonymous communication channel over Tor~\cite{dingledineTorSecondGenerationOnion2004} and blind signatures~\cite{chaumSecurityIdentificationTransaction1985}. Fair exchange, physical delivery, and dispute resolution is achieved using delivery cabinet (DC) under the seller's control (e.g. Amazon Locker) and offline TTP that intervenes only in the case of a dispute.

The protocol works as follows:

\begin{enumerate}
    \item The buyer buys a digital coin from his bank, blind signature is used to preserve customer's privacy.
    \item The buyer sends to the seller the purchase details, address of DC, customer's bank signature, and some meta data to preserve the integrity of transaction, communication is done over Tor.
    \item The seller request a redemption of the digital coin.
    \item The seller posts the product to the DC via delivery serivice.
    \item The DA collects the product from the SC and posts it to the DC.
    \item The buyer collects the product from the DC using a password.
    \item The buyer checks if the product is the ordered one, if not, opens a dispute to TTP.
\end{enumerate}

Besides the assumptions of the existence of the TTP, the protocol also assumes:

\begin{itemize}
    \item the buyer's and seller's banks enable confidential transactions, and both share a commit buffer where the value is locked until the transaction is finished;
    \item banks maintain a global list of coins' serial numbers to prevent double-spending problems;
    \item there exists an anonymous communication channel, and the SC and the DC protected by a passwords;
    \item the DC is equipped with a video camera that records the moment when the buyer opens the package and provides a way to submit the video to TTP in case of a dispute;
\end{itemize}

@@

However, since the system uses Ethereum, it achieves pseudonymity rather than anonymity (see Section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.

@@

Also, we didn't put much attention to the protocols for buying digital products as they are not relevant to our use case. The comprehensive analysis of such protocols is avaiable in~\cite{birjoveanuTwoPartyECommerceProtocols2022}.

@@

Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, however, it is based on strong assumptions, namely, existence of TTP, banks supporting confidental transactions with commit buffers, and mantainng a global list of coins' serial numbers.

Our protocol achieves anonymity by using either cash or privacy-preserving blockchains. Moreover, our protocol does not require a customer to submit any transaction to the message board, which in other protocols may be the weakest link in achieving the anonymity.

Moreover, none of them directly address our use case. We want the SP to remain public so that the anonymous buyer can easily start a dispute. We assume just one package of physical materials. Moreover, the package is delivered from the buyer to the SP, not the other way around — as it's the case for most e-commerce transactions.

Also, our protocol does not provide its own dispute-resolution mechanism as Themis does. However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party. 
It can be instantiated with either the local court or police, or one of the blockchain
dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan. 10, 2023)}, LTO Network\footnote{LTO Network, a hybrid blockchain application development platform for securing, verifying, and exchanging enterprise information, https://lto.network/, (last visited Jan. 17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.

@@

The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature, but is based on strong or unpractical assumptions.

\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{table*}}{\begin{table}}
\centering
\newcommand{\YES}{\cellcolor{green!50}Yes}
\newcommand{\YESBUT}{\cellcolor{green!25}Yes*}
\newcommand{\ID}{\cellcolor{green!25}Identity}
\newcommand{\PSEUDO}{\cellcolor{green!35}Pseudonym}
\newcommand{\ANON}{\cellcolor{green!50}Anonymity}
\newcommand{\NO}{\cellcolor{red!50}No}
\newcommand{\TTP}{\cellcolor{red!50}TTP}
\newcommand{\BC}{\cellcolor{green!50}BC}
\newcommand{\BCBUT}{\cellcolor{green!35}BC*}
\caption{Comparision of related works.}
\label{tab:comparision}
\setlength{\tabcolsep}{3pt}

@@

\hline
Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
\hline
Zhang et al. 2006~\cite{zhangPracticalFairExchangeEPayment2006} & \YES & \YESBUT & \YES & \TTP & \YES \\
\hline
Alaraj, 2012~\cite{mohammedalarajFairnessPhysicalProducts2012} & \YESBUT & \NO & \YES & \TTP & \YES \\
\hline
Lelantos, 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
\hline
Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
\hline
Themis, 2019~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
\hline
PPPDCP, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} & \YES & \YES & \YES & \TTP & \YES \\
\hline
This paper & \YES & \YES & \YES & \BCBUT & \YES \\
\hline

@@

\section{Building Blocks}\label{sec:building-blocks}

\subsection{Physical products}\label{sec:physical-products}
The use cases we address in this paper use physical materials like blood, urine, hair, and other biological materials.
This requirement, combined with the requirement of anonymity, is a challenging part of the fair-exchange protocols. The problem arises when the seller wants to sent the product to the buyer who wants to remain anonymous. Most of the existing protocols either assume the existence of trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use complex delivery mechanism similar to onion rounting involving multiple many delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

However, our use case is different in that the physical materials are transfered from the (anonymous) customer to the (public) SP. This, allows for siplification of the delivery process. We assume that there is a way to anonymously deliver a package without revealing the customer personal information either via SP's drop box, Parcel Locker services (e.g. Amazon Locker, InPost\footnote{InPost, Parcel locker service, \url{https://inpost.pl/en}, \LASTVISITED}), a customer's trusted party, of even post office.

\subsection{Dispute resolution system}
\label{sec:dispute-resolution}

@@

Some oracles provide the data like weather, soccer match result, stock
price, train delay, election results, and others—and they are the ones we
are interested in—provide the settlement of a submitted dispute.

@@

Such a decentralized, voluntary, and anonymous dispute resolution system might work for simple contracts violations like an eBay seller sending broken or wrong products or an Airbnb apartment being inadequate to the photos in the offer. However, it is hard to realize such a decentralized evaluation of health or legal services quality when expertise and privacy concerns are taken into account. Therefore, in our protocol, we take a more conservative approach and resolve disputes by recording evidence on blockchain and then using the local justice system (police or court) to settle the conflict.

@@

    \item Payment $\mathrm{receipt}$ is confirmation that the customer has paid for the transaction at a certain time. The actual implementation depends on the particular cryptocurrency and is discussed further Section~\ref{payment-for-services}.

@@

\subsection{Payment for services}\label{payment-for-services}
Transactions between customers and SPs must be pegged to prevent reusing one payment for multiple transactions. 
In other words, we need a mechanism that uniquely associates a payment with the corresponding transaction.

Depending on the cryptocurrency, the link can be created in different
ways:

\item separate address: each transaction uses an unique address associated with the transaction. Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{Bitcoin Improvement Proposals, Hierarchical Deterministic Wallets, \url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}, (last visited Dec. 03, 2022)} and published on message board, to achieve non-repudiation.
\item memo: the payments are sent to sigle SP account, but contain an extra field named ``memo'' filled with the unique indentifier $\textrm{provisionID}$. 
\end{itemize}

Each payment containing the $\textrm{provisionID}$ in the memo, or payment to the dedicated address is considered to pay for the transaction.

In case of a dispute, there must be a way to prove to justice that the customer has paid for the transaction. As the proof of payment is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains. Monero allows proving and checking payments via dedicated API\footnote{Monero, How to prove payment, \url{https://www.getmonero.org//resources/user-guides/prove-payment.html}, \LASTVISITED}. ZCash provides a mechanism called Payment Disclosure \footnote{Gareth Davies, An Introduction to Payment Disclosure in Zcash, \url{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}, \LASTVISITED}. We call the proof of payment a \textit{payment recepit}.

\subsection{Storage network}\label{storage-network}
Once the SP finishes its service, she has to provide the result to the customer. The most natural approach would be to send the result via e-mail or some dedicated platform. However, the customer wants to stay anonymous and so does not want to expose his e-mail address nor IP address. Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in Section ~\ref{sec:message-board}.

@@

To increase anonymity, the customer should use standard techniques to hide its IP address, such as VPN, or proxy.

@@

While most blockchains could provide message board functionality, anonymous payments are not as common. Especially a provable storage network is a functionality of a few specialized blockchains.

@@

\section{The Protocol}\label{sec:protocol}
In this section, we propose an abstract protocol for anonymous service provisioning without any assumptions about the underlying technologies. We define the requirements for each role and leave the choice of the technology to the developer. Later in the paper (Section~\ref{sec:experiments}) we describe our implementation used to conduct an experiment.

@@

\begin{itemize}
\item There exists PKI infrastructure:
    \begin{itemize}
        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP accordingly.
        \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}(\mathrm{C})}$ and the SP $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$.
        \item The SP's public key $\mathrm{pk}(\mathrm{SP})$ is publicly known.
    \end{itemize}

\item Both the customer and the SP:
    \begin{itemize}
        \item use common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
        \item have access to anonymous payments blockchain, message board, and storage network.
    \end{itemize}

\item The SP:
    \begin{itemize}
        \item accepts packages from unknown customers.
        \item accepts payments with cash and anonymous cryptocurrencies as described in Section~\ref{payment-for-services}.
    \end{itemize}

\item Justice:
    \begin{itemize}
        \item accepts as evidence in a dispute the $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{receipt}$ as described in Section~\ref{fairness}.
    \end{itemize}

\item Anonymous payments blockchain:
    \begin{itemize}
        \item supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in Section~\ref{sec:pseudo-anon}.
        \item supports uniquely identifying transactions via a dedicated address, memo field, or other similar mechanisms as described in Section ~\ref{payment-for-services}. 
    \end{itemize}

@@

\noindent \textbf
{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service.

@@

@@

also:
\(\mathrm{T}_\mathrm{issue} \leq \mathrm{T}_\mathrm{pay} \leq \mathrm{T}_\mathrm{provide}\)

@@

\item $\mathrm{cid}$ - content identifier as specified in Section~\ref{storage-network}.
\item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
\end{itemize}

\noindent \textbf
{Payment receipt}\label{payment-receipt} proves that the customer did the payment. Since the evidence depends on a particular blockchain (see Section~\ref{payment-for-services}), we refer to it symbolically as
$\mathrm{receipt}$.
